Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-12 SupportingInformation.Rmd
skewness plot axis labels fixed

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman")

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=T,
                          corpres="spearman") 
p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=T,
                           corpres="spearman") 
p_left<-sum(answer1s$surrogskw < answer1s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

>>>>

pdf("./Results/skewness_results/skewness_aphid_count/skewness_aphid_count_sp_10_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=10,d_allsp=data_aphid_count),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)

@@

pdf("./Results/skewness_results/skewness_aphid_ff/skewness_aphid_ff_sp_11_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer2s<-skewness_testing(ts_matrix=sp_data(sp=11,d_allsp=data_aphid_ff),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman")
hist(answer2s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer2s$realskw,y=0,col="black",pch=15,cex=2)

p_right<-sum(answer2s$surrogskw > answer2s$realskw)/numsurrog
mtext(paste0("p = ",p_right),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_plankton_north_sea/skewness_plankton_north_sea_sp_16_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer3s<-skewness_testing(ts_matrix=sp_data(sp=16,d_allsp=data_plankton_north_sea),loclist=loclist,numsurrog=numsurrog,ploton=F,
                          corpres="spearman") 
hist(answer3s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer3s$realskw,y=0,col="black",pch=15,cex=2)

p_left<-sum(answer3s$surrogskw < answer3s$realskw)/numsurrog
mtext(paste0("p = ",p_left),side=3,line=-0.5,cex = 2)
par(op)
dev.off()
```

@@

pdf("./Results/skewness_results/skewness_methane/skewness_methane_spearman.pdf",height=6,width=8)
op<-par(mar=c(5,5,1.8,0.1), mgp=c(3, 1, 0))
answer1s<-skewness_testing(ts_matrix=sp_data(sp=1,d_allsp=methane_data),loclist=loclist,numsurrog=numsurrog,ploton=F,
                           corpres="spearman") 
hist(answer1s$surrogskw,breaks=100,main="",xlab="Skewness",ylab="Frequency",cex.lab=2,cex.axis=2,col="grey",border=F)
#abline(v=realskw,col="red")
points(x=answer1s$realskw,y=0,col="black",pch=15,cex=2)
